Modelling BCG vaccination in the UK

### 2019-07-31 rmds/09-model-fitting.Rmd
table formating

```{r 09-fig-prior-params, fig.scap = "Prior and posterior distributions for fitted model parameters.", fig.cap = "Prior and posterior distributions for fitted model parameters. Parameter names in figure are in their coded form. They can be interpreted using the following: beta_young_adult - $\\beta_{\\text{young adult}}$"}
knitr::include_graphics(file.path(plots_path, "prior-posterior-overview-1.png"))
```

>>>>

```{r 09-fig-prior-params, fig.scap = "Prior and posterior distributions for fitted model parameters.", fig.cap = "Prior and posterior distributions for fitted model parameters. Parameter names in figure are in their coded form. They can be interpreted using the following: beta_young_adult"}
knitr::include_graphics(file.path(plots_path, "prior-posterior-overview-1.png"))
```
